Reduced Nucleotide Diversity on a Plant Y Chromosome Following Recent Recombination Suppression

### 2016-07-27 manusctipt.tex
bib fix
readme edits, minor ms changes
neutral predictions section and bib

\subsection*{Neutral predictions and the effect of sex ratio bias on diversity} 
Wright's (1931) formula $N_{e}=4N_{f}N_{m}/(N_{f} + N_{m})$ gives the effective population size of a randomly mating population with separate sexes and a Poisson distribution of offspring number

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{Figure1.png}
\caption{Example figure from \url{10.1534/genetics.114.173807}. Please include your figures in the manuscript for the review process. You can upload figures to Overleaf via the Project menu. Upon acceptance, we'll ask for your figure files to be uploaded in any of the following formats: TIFF (.tiff), JPEG (.jpg), Microsoft PowerPoint (.ppt), EPS (.eps), or Adobe Illustrator (.ai).  Images should be a minimum of 300 dpi in resolution and 500 dpi minimum if line art images.  RGB, CMYK, and Grayscale are all acceptable. Halftones should be high contrast with sharp detail, because some loss of detail and contrast is inevitable in the production process. Figures should be 10-20 cm in width and 1-25 cm in height. Graph axes must be exactly perpendicular and all lines of equal density.
Label multiple figure parts with A, B, etc. in bolded type, and use Arrows and numbers to draw attention to areas you want to highlight. Legends should start with a brief title and should be a self-contained description of the content of the figure that provides enough detail to fully understand the data presented. All conventional symbols used to indicate figure data points are available for typesetting; unconventional symbols should not be used. Italicize all mathematical variables (both in the figure legend and figure) , genotypes, and additional symbols that are normally italicized.  
}%
\label{fig:spectrum}
\end{figure}

@@

\bibliography{example-bibliography}
\end{document}

>>>>

\subsection*{Neutral predictions and the effect of sex ratio bias on diversity}
Wright's (1931) formula $N_{e}=4N_{f}N_{m}/(N_{f} + N_{m})$ gives the effective population size of a randomly mating population with separate sexes and a Poisson distribution of offspring number. For a female effective population size $N_{f}$, and a male effective population size $N_{m}$, the predicted effective population size for X-linked genes relative to autosomes is given by $N_{e_{X}}/N_{e_{A}} = 9(N_{f}+N_{m})/8(2N_{f}+N_{m})$ (Wright 1931). In a neutral model with equal sex ratios, $N_{e_{X}}/N_{e_{A}} = 0.75$. For populations with female-biased sex ratios, however, $N_{m}$ becomes small relative to $N_{f}$ and this ratio can become larger than 1, approaching 1.125 at the limit \citep{caballero1995}. For the Y chromosome, the effective population size is given by 1/4 the total $N_{e}$ or 1/2 the $N_{e}$ of males, $N_{m}$/2. Under neutrality, the level of nucleotide polymorphism maintained in a population is proportional to the product of the mutation rate and the effective population size: $\theta=4N_{e}\mu$ \citep{watterson1975,kimura1984}. Assuming equal neutral mutation rates for all genes and an equal number of reproducing males and females, Y-linked genes should therefore have 1/3 the polymorphism of X-linked genes, and 1/4 that of autosomal genes. Figure 1 shows the predicted relative effective population size ratios for autosomal, X-linked, and Y-linked genes (left) and the corresponding X/A and Y/A ratios of diversity (right) for a sex ratio bias ranging from $N_{f}/(N_{f}+N_{m})=0$ to $N_{f}/(N_{f}+N_{m})=1$.

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{Figure1.png}
\caption{\textbf{A:} The relation between relative effective population size and sex ratio bias for genes on autosomes (A), X chromosomes (X), and Y chromosomes (Y). The sex ratio is shown as the proportion of females, $N_{f}/(N_{f}+N_{m})=0$, ranging from 0 to 1, where $N_{m}$ and $N_{f}$ are the effective number of breeding males and females, respectively. Calculations assume a constant population size, non-overlapping generations, and a Poisson distribution of offspring number \citep{wright1931evolution,charlesworth2009effective}. The $N_{e}$ for each chromosome type is calculated relative to the predicted $N_{e}$ for genes on autosomes with an equal sex ratio.\textbf{B:} The corresponding expected relation between sex ratio bias and the sex-chromosome-to-autosome diversity ratio, assuming $\theta=4N_{e}\mu$ and equal neutral mutation rates for all genes.
}%
\label{fig:spectrum}
\end{figure}

@@

@@

\bibliography{bibliography}
\end{document}
